Tampering Detection In Low-Power Smart Cameras

### 2015-05-18 paper.tex
problem formulation --draft

Let us denote by $z_t$ the frame that acquired at time $t$, which we model as
\begin{equation}
\label{eq:observationModel}
z_t(x)=\mathcal{D}_t[y_t](x) \forall x \in X
\end{equation}
where $\mathcal{D}$ denotes the degradation operator, which transforms the original frame $y_t$ in our observation; $X \subset \mathbb{Z}$ denotes the regular pixels grid and $x$ is a vector indicating the pixel coordinates. When there is no tampering, the frame 
\begin{equation}
\label{eq:no tampering}
\mathcal{D}_t[y_t](x) = y_t(x) + \eta_t(x) \forall x \in X
\end{equation}
where $\eta_t$ is a random variable accounting for all the noise sources (thermal, quantization, photon-counting).

However, when the camera 
\begin{equation}
\label{eq:defocus}
\mathcal{D}_t[y_t](x) = \mathcal{B}_t[y_t](x) + \eta_t(x) \forall x \in X
\end{equation}

\begin{equation}
\label{eq:blur}
\mathcal{B}[y](x) = \int_{\mathcal{X}}y(s)h(x,s)ds,
\end{equation}

\begin{equation}
\label{eq:blur_convolution}
\mathcal{B}[y](x) = \int_{\mathcal{X}}y(s)h(s-x)ds,
\end{equation}

\begin{equation}
\label{eq:blur_multi}
z_t(x)=\mathcal{D}_t[y_t](x) = \mathcal{B}_t[y_t](x) + \eta(x), \qquad x \in \mathcal{X}.
\end{equation}

\begin{equation}
\label{eq:displacement}
z_t(x)  = \left\{ \begin{array}{rcl}
y_t(x) + \eta(x) & \mbox{per} & t < T^* \\
w_t(x) + \eta(x) & \mbox{per} & t \geqslant T^*
\end{array}\right. ,
\end{equation}

Per $t<T^*$ abbiamo che i frame vengono acquisiti in condizioni di funzionamento normale:
\[ z_t(x)=y_t(x) + \eta(x), \forall x \in \mathcal{X} \mbox{, per } t=1,\dots , T^*-1. \] 
All'istante di tempo $t = T^*$ avviene un evento di tampering, il quale compromette i frame per $t\geq T^*$.  
In particolare, nel caso di una sfocatura avremo
\[ z_t = \mathcal{B}_t[y_t](x) + \eta(x), \forall x \in \mathcal{X} \mbox{, per } t \geq T^*,\]
mentre nel caso di uno spostamento della camera avremo
\[ z_t = w_t(x) + \eta(x), \forall x \in \mathcal{X} \mbox{, per } t \geq T^*. \]

>>>>

Let us denote by $z_t$ the frame acquired at time $t$, which we model as
\begin{equation}
\label{eq:observationModel}
z_t(x)=\mathcal{D}_t[y_t](x) \quad \forall x \in X
\end{equation}
where $\mathcal{D}_t$ denotes the degradation operator that transforms the original image $y_t$ in the frame $z_t$ which we acquire; $X \subset \mathbb{Z}$ denotes the regular pixels grid and $x$ is a vector indicating the pixel coordinates. As far as there is no tampering attacks/events,
\begin{equation}
\label{eq:no_tampering}
\mathcal{D}_t[y_t](x) = y_t(x) + \eta_t(x) \quad \forall x \in X
\end{equation}
where $\eta_t$ is a random variable accounting for all the noise sources (thermal, quantization, photon-counting). In normal conditions, all the images $y_t$ (thus also the frames $z_t$) might be different in content but are acquired from the same viewpoint and the same camera orientation.

When at time $\tau^*$ an external disturbance over the camera lens introduces a defocus, the image $y_t$ is blurred by spatially variant operator:
\begin{equation}
\label{eq:model_defocus}
\mathcal{D}_t[y_t](x) = \int_{\mathcal{X}}y(s)h_t(x,s)ds\, + \eta_t(x) \quad \forall x \in X, t \leq \tau^*
\end{equation}
%where  $\mathcal{B}_t$ corresponds to a linear operator
%\begin{equation}
%\label{eq:blur}
%\mathcal{B}[y](x) = \int_{\mathcal{X}}y(s)h(x,s)ds\,,
%\end{equation}
where $h_t(x,\cdot) > 0$ is the point-spread function at pixel $x \in X$.

%\begin{equation}
%\label{eq:blur_convolution}
%\mathcal{B}[y](x) = \int_{\mathcal{X}}y(s)h(s-x)ds,
%\end{equation}
%
%\begin{equation}
%\label{eq:blur_multi}
%z_t(x)=\mathcal{D}_t[y_t](x) = \mathcal{B}_t[y_t](x) + \eta(x), \qquad x \in \mathcal{X}.
%\end{equation}
A camera displacement at frame $\tau^*$ is modeled as 
\begin{equation}
\label{eq:model_displacement}
z_t(x)  = \left\{ \begin{array}{rcl}
y_t(x) + \eta(x) & \mbox{per} & t < T^* \\
w_t(x) + \eta(x) & \mbox{per} & t \geqslant T^*
\end{array}\right. ,
\end{equation}
where $w_t$ is acquired from a different viewpoint and/or camera orientation than $y_t$.

The proposed tampering-detection algorithm analyzes a sequence of frames $\{z_t\}_t$ and detect frames at time $\tau^*$ that correspond to a tampering like \eqref{eq:model_defocus} or \eqref{eq:model_displacement}.

%Per $t<T^*$ abbiamo che i frame vengono acquisiti in condizioni di funzionamento normale:
%\[ z_t(x)=y_t(x) + \eta(x), \forall x \in \mathcal{X} \mbox{, per } t=1,\dots , T^*-1. \] 
%All'istante di tempo $t = T^*$ avviene un evento di tampering, il quale compromette i frame per $t\geq T^*$.  
%In particolare, nel caso di una sfocatura avremo
%\[ z_t = \mathcal{B}_t[y_t](x) + \eta(x), \forall x \in \mathcal{X} \mbox{, per } t \geq T^*,\]
%mentre nel caso di uno spostamento della camera avremo
%\[ z_t = w_t(x) + \eta(x), \forall x \in \mathcal{X} \mbox{, per } t \geq T^*. \]
